---
title: "<span class='badge-naia'>NAIA</span><br><span class='title-main'>Women's Wrestling</span><br><span class='title-accent'>Championships</span>"
subtitle: "Explore 1,600+ historic bouts, 50 collegiate programs nationwide, and every national podium finish (2019–2026)."
---

From buzzer-beating pins to dominant title runs, explore the athletes and programs defining collegiate women's wrestling. Hover or click on the map to discover schools across the nation.

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(reactable)
library(htmltools)
library(leaflet)
library(plotly)

# Read all-time match results
all_matches <- read_csv("data/naia_matches_all_years.csv", show_col_types = FALSE)

# Read school coordinates for geography map
schools_geo <- read_csv("data/naia_schools_geo.csv", show_col_types = FALSE)

# Color badge helper for win method
badge_win_method <- \(value) {
  if (is.na(value) || value == "") return("")
  val <- tolower(as.character(value))
  col <- if (grepl("fall|vfa", val)) "#dc2626" else if (grepl("tf|tech|vsu", val)) "#7c3aed" else if (grepl("dec|vpo", val)) "#2563eb" else "#64748b"
  tags$span(
    style = sprintf("display: inline-block; padding: 2px 8px; border-radius: 9999px; font-size: 0.75rem; font-weight: 600; background: %s18; color: %s;", col, col),
    value
  )
}

# Badges to emphasize champions and podium medalists
badge_champion <- \(value) {
  if (is.na(value) || value == "") return("")
  tags$span(
    style = "display: inline-block; font-weight: 700; color: #92400e; background: #fef3c7; border: 1px solid #fde68a; border-radius: 6px; padding: 3px 10px;",
    paste0("🥇 ", value)
  )
}

badge_runner_up <- \(value) {
  if (is.na(value) || value == "") return("")
  tags$span(
    style = "display: inline-block; font-weight: 600; color: #475569; background: #f1f5f9; border: 1px solid #e2e8f0; border-radius: 6px; padding: 3px 8px;",
    paste0("🥈 ", value)
  )
}

badge_place <- \(value) {
  if (is.na(value) || value == "") return("")
  if (grepl("1st", value)) {
    tags$span(
      style = "display: inline-block; font-weight: 800; color: #92400e; background: #fef3c7; border: 1.5px solid #f59e0b; border-radius: 9999px; padding: 3px 12px; font-size: 0.85rem;",
      value
    )
  } else if (grepl("2nd", value)) {
    tags$span(
      style = "display: inline-block; font-weight: 700; color: #334155; background: #f1f5f9; border: 1px solid #cbd5e1; border-radius: 9999px; padding: 2px 10px; font-size: 0.85rem;",
      value
    )
  } else if (grepl("3rd", value)) {
    tags$span(
      style = "display: inline-block; font-weight: 700; color: #9a3412; background: #ffedd5; border: 1px solid #fdba74; border-radius: 9999px; padding: 2px 10px; font-size: 0.85rem;",
      value
    )
  } else {
    tags$span(
      style = "display: inline-block; font-weight: 600; color: #64748b; background: #f8fafc; border: 1px solid #e2e8f0; border-radius: 9999px; padding: 2px 8px; font-size: 0.8rem;",
      value
    )
  }
}

badge_state <- \(value) {
  if (is.na(value) || value == "") return("")
  tags$span(
    style = "display: inline-block; padding: 2px 8px; border-radius: 9999px; font-size: 0.75rem; font-weight: 700; background: #e0f2fe; color: #0284c7; border: 1px solid #bae6fd;",
    value
  )
}

badge_champ_count <- \(value) {
  if (value > 0) {
    tags$span(
      style = "display: inline-block; font-weight: 700; color: #92400e; background: #fef3c7; border: 1px solid #fde68a; border-radius: 6px; padding: 2px 8px;",
      paste0("👑 ", value)
    )
  } else {
    tags$span(style = "color: #94a3b8;", "0")
  }
}

badge_aa_count <- \(value) {
  if (value > 0) {
    tags$span(
      style = "display: inline-block; font-weight: 600; color: #0f172a; background: #f1f5f9; border: 1px solid #cbd5e1; border-radius: 6px; padding: 2px 8px;",
      paste0("🎖️ ", value)
    )
  } else {
    tags$span(style = "color: #94a3b8;", "0")
  }
}

# Theme for the tables
tbl_theme <- reactableTheme(
  borderColor = "#e2e8f0",
  stripedColor = "#f8fafc",
  highlightColor = "#eff6ff",
  cellPadding = "8px 12px",
  headerStyle = list(
    backgroundColor = "#f8fafc",
    borderBottom = "2px solid #cbd5e1",
    fontWeight = 600,
    fontSize = "0.875rem",
    color = "#334155"
  )
)

# Extract podium placements from medal rounds across all years
is_1st <- all_matches$round == "Finals" | grepl("^1st Place", all_matches$round)
is_3rd <- grepl("^3rd Place", all_matches$round)
is_5th <- grepl("^5th Place", all_matches$round)
is_7th <- grepl("^7th Place", all_matches$round)

placements <- bind_rows(
  all_matches[is_1st, ] |> transmute(year, weight_class, wrestler = winner, place = "👑 Champion"),
  all_matches[is_1st, ] |> transmute(year, weight_class, wrestler = loser, place = "🥈 2nd Place"),
  all_matches[is_3rd, ] |> transmute(year, weight_class, wrestler = winner, place = "🥉 3rd Place"),
  all_matches[is_3rd, ] |> transmute(year, weight_class, wrestler = loser, place = "🏅 4th Place"),
  all_matches[is_5th, ] |> transmute(year, weight_class, wrestler = winner, place = "🏅 5th Place"),
  all_matches[is_5th, ] |> transmute(year, weight_class, wrestler = loser, place = "🏅 6th Place"),
  all_matches[is_7th, ] |> transmute(year, weight_class, wrestler = winner, place = "🏅 7th Place"),
  all_matches[is_7th, ] |> transmute(year, weight_class, wrestler = loser, place = "🏅 8th Place")
) |> distinct(year, weight_class, wrestler, .keep_all = TRUE)

# Count total career podium placements per wrestler
placer_counts <- placements |>
  count(wrestler, name = "times_placed")

# Normalize school names to map accurately to institutional geography
map_to_geo <- function(x) {
  s <- str_remove_all(x, "\\s*\\([A-Za-z0-9\\.\\s]+\\)")
  s <- str_trim(s)
  case_when(
    grepl("^Life Pacific", s) ~ NA_character_,
    grepl("^Life", s) ~ "Life University",
    grepl("^Southern Oregon", s) ~ "Southern Oregon University",
    grepl("^Cumberlands|^University of Cumberlands", s) ~ "University of the Cumberlands",
    grepl("^Grand View", s) ~ "Grand View University",
    grepl("^Campbellsville", s) ~ "Campbellsville University",
    grepl("^Providence", s) ~ "University of Providence",
    grepl("^Missouri Valley", s) ~ "Missouri Valley College",
    grepl("^Oklahoma City", s) ~ "Oklahoma City University",
    grepl("^Menlo", s) ~ "Menlo College",
    grepl("^William Penn", s) ~ "William Penn University",
    grepl("^Indiana Tech", s) ~ "Indiana Tech",
    grepl("^Wayland Baptist|^Oviance", s) ~ "Wayland Baptist University",
    grepl("^Ottawa", s) ~ "Ottawa University",
    grepl("^Eastern Oregon", s) ~ "Eastern Oregon University",
    grepl("^Texas Wesleyan", s) ~ "Texas Wesleyan University",
    grepl("^Jamestown", s) ~ "University of Jamestown",
    grepl("^Missouri Baptist", s) ~ "Missouri Baptist University",
    grepl("^Hastings", s) ~ "Hastings College",
    grepl("^Baker", s) ~ "Baker University",
    grepl("^Midland", s) ~ "Midland University",
    grepl("^Lyon", s) ~ "Lyon College",
    grepl("^Saint Mary|^St. Mary|^University of St", s) ~ "University of Saint Mary",
    grepl("^Waldorf", s) ~ "Waldorf University",
    grepl("^Lindsey Wilson", s) ~ "Lindsey Wilson College",
    grepl("^Doane", s) ~ "Doane University",
    grepl("^York", s) ~ "York University",
    grepl("^Central Methodist", s) ~ "Central Methodist University",
    grepl("^Brewton", s) ~ "Brewton-Parker College",
    grepl("^Corban", s) ~ "Corban University",
    grepl("^Avila", s) ~ "Avila University",
    grepl("^Central Christian", s) ~ "Central Christian College",
    grepl("^Dickinson", s) ~ "Dickinson State University",
    grepl("^Friends", s) ~ "Friends University",
    grepl("^Evergreen", s) ~ "Evergreen State College",
    grepl("^Lourdes", s) ~ "Lourdes University",
    grepl("^Vanguard", s) ~ "Vanguard University",
    grepl("^Simpson", s) ~ "Simpson University",
    grepl("^Bismarck", s) ~ "Bismarck State College",
    grepl("^St. Andrews", s) ~ "St. Andrews University",
    grepl("^Westcliff", s) ~ "Westcliff University",
    grepl("^William Woods", s) ~ "William Woods University",
    grepl("^Montreat", s) ~ "Montreat College",
    grepl("^Siena Heights", s) ~ "Siena Heights University",
    grepl("^Arizona Christian", s) ~ "Arizona Christian University",
    grepl("^Dakota Wesleyan", s) ~ "Dakota Wesleyan University",
    grepl("^Georgetown", s) ~ "Georgetown College",
    grepl("^Jarvis Christian", s) ~ "Jarvis Christian University",
    grepl("^Rio Grande", s) ~ "University of Rio Grande",
    grepl("^Rochester", s) ~ "Rochester Christian University",
    grepl("^Iowa Wesleyan", s) ~ "Iowa Wesleyan University",
    grepl("^Lincoln", s) ~ "Lincoln College",
    grepl("^Warner Pacific", s) ~ "Warner Pacific University",
    TRUE ~ s
  )
}

# Calculate tournament records (Wins - Losses) for each wrestler
records_df <- bind_rows(
  all_matches |> transmute(year, weight_class, wrestler = winner, res = "W"),
  all_matches |> transmute(year, weight_class, wrestler = loser, res = "L")
) |>
  filter(!is.na(wrestler), wrestler != "") |>
  group_by(year, weight_class, wrestler) |>
  summarize(
    record = paste0(sum(res == "W"), "-", sum(res == "L")),
    .groups = "drop"
  )

fmt_bout <- function(lead, opp, score, method) {
  sc <- if_else(is.na(score) | score == "", method, score)
  paste0(lead, " ", opp, " (", sc, ")")
}

# Build National Placers dataset (1st through 8th place finishes)
placers_df <- bind_rows(
  all_matches[is_1st, ] |> transmute(year, weight_class, place_num = 1, place = "🥇 1st Place", wrestler = winner, school = map_to_geo(winner_school), medal_bout = fmt_bout("Def.", loser, score, win_method)),
  all_matches[is_1st, ] |> transmute(year, weight_class, place_num = 2, place = "🥈 2nd Place", wrestler = loser, school = map_to_geo(loser_school), medal_bout = fmt_bout("Finalist vs.", winner, score, win_method)),
  all_matches[is_3rd, ] |> transmute(year, weight_class, place_num = 3, place = "🥉 3rd Place", wrestler = winner, school = map_to_geo(winner_school), medal_bout = fmt_bout("Def.", loser, score, win_method)),
  all_matches[is_3rd, ] |> transmute(year, weight_class, place_num = 4, place = "4th Place", wrestler = loser, school = map_to_geo(loser_school), medal_bout = fmt_bout("vs.", winner, score, win_method)),
  all_matches[is_5th, ] |> transmute(year, weight_class, place_num = 5, place = "5th Place", wrestler = winner, school = map_to_geo(winner_school), medal_bout = fmt_bout("Def.", loser, score, win_method)),
  all_matches[is_5th, ] |> transmute(year, weight_class, place_num = 6, place = "6th Place", wrestler = loser, school = map_to_geo(loser_school), medal_bout = fmt_bout("vs.", winner, score, win_method)),
  all_matches[is_7th, ] |> transmute(year, weight_class, place_num = 7, place = "7th Place", wrestler = winner, school = map_to_geo(winner_school), medal_bout = fmt_bout("Def.", loser, score, win_method)),
  all_matches[is_7th, ] |> transmute(year, weight_class, place_num = 8, place = "8th Place", wrestler = loser, school = map_to_geo(loser_school), medal_bout = fmt_bout("vs.", winner, score, win_method))
) |>
  distinct(year, weight_class, place_num, .keep_all = TRUE) |>
  left_join(records_df, by = c("year", "weight_class", "wrestler")) |>
  mutate(record = replace_na(record, "—")) |>
  arrange(desc(year), weight_class, place_num)

# Yearly participation and program growth
growth_df <- bind_rows(
  all_matches |> transmute(year, wrestler = winner, school = winner_school),
  all_matches |> transmute(year, wrestler = loser, school = loser_school)
) |>
  filter(!is.na(wrestler), wrestler != "") |>
  group_by(year) |>
  summarize(
    Athletes = n_distinct(wrestler),
    Colleges = n_distinct(school[school != "" & school != "Unknown"]),
    .groups = "drop"
  )

matches_norm <- all_matches |>
  mutate(
    norm_winner_school = map_to_geo(winner_school),
    norm_loser_school = map_to_geo(loser_school)
  )

all_school_placers <- bind_rows(
  matches_norm[is_1st, ] |> transmute(year, weight_class, place = "1st Place", wrestler = winner, school = norm_winner_school),
  matches_norm[is_1st, ] |> transmute(year, weight_class, place = "2nd Place", wrestler = loser, school = norm_loser_school),
  matches_norm[is_3rd, ] |> transmute(year, weight_class, place = "3rd Place", wrestler = winner, school = norm_winner_school),
  matches_norm[is_3rd, ] |> transmute(year, weight_class, place = "4th Place", wrestler = loser, school = norm_loser_school),
  matches_norm[is_5th, ] |> transmute(year, weight_class, place = "5th Place", wrestler = winner, school = norm_winner_school),
  matches_norm[is_5th, ] |> transmute(year, weight_class, place = "6th Place", wrestler = loser, school = norm_loser_school),
  matches_norm[is_7th, ] |> transmute(year, weight_class, place = "7th Place", wrestler = winner, school = norm_winner_school),
  matches_norm[is_7th, ] |> transmute(year, weight_class, place = "8th Place", wrestler = loser, school = norm_loser_school)
) |>
  filter(!is.na(school), school != "")

school_placers_summary <- all_school_placers |>
  group_by(school) |>
  summarize(
    national_champions = sum(grepl("1st", place)),
    all_americans = n(),
    .groups = "drop"
  )

school_bouts_summary <- bind_rows(
  matches_norm |> transmute(school = norm_winner_school, result = "Win"),
  matches_norm |> transmute(school = norm_loser_school, result = "Loss")
) |>
  filter(!is.na(school), school != "") |>
  group_by(school) |>
  summarize(
    total_bouts = n(),
    bouts_won = sum(result == "Win"),
    win_pct = paste0(round(bouts_won / total_bouts * 100), "%"),
    .groups = "drop"
  )

school_legacy_table <- schools_geo |>
  left_join(school_placers_summary, by = "school") |>
  left_join(school_bouts_summary, by = "school") |>
  mutate(
    national_champions = replace_na(national_champions, 0),
    all_americans = replace_na(all_americans, 0),
    bouts_won = replace_na(bouts_won, 0),
    total_bouts = replace_na(total_bouts, 0),
    win_pct = replace_na(win_pct, "0%")
  ) |>
  arrange(desc(national_champions), desc(all_americans), desc(bouts_won))

# Build roster per tournament appearance
roster_df <- bind_rows(
  all_matches |> transmute(year, weight_class, wrestler = winner, school = winner_school, result = "Won"),
  all_matches |> transmute(year, weight_class, wrestler = loser, school = loser_school, result = "Lost")
) |>
  filter(!is.na(wrestler), wrestler != "") |>
  group_by(year, weight_class, wrestler) |>
  summarize(
    school = {
      s <- na.omit(school)
      s <- s[s != "" & s != "Unknown"]
      if (length(s) > 0) s[length(s)] else "—"
    },
    wins = sum(result == "Won"),
    losses = sum(result == "Lost"),
    record = paste0(wins, "-", losses),
    .groups = "drop"
  ) |>
  left_join(placements, by = c("year", "weight_class", "wrestler")) |>
  mutate(place = replace_na(place, "Competitor")) |>
  arrange(desc(year), weight_class, desc(wins))

total_matches <- format(nrow(all_matches), big.mark = ",")
total_tournaments <- n_distinct(all_matches$year)
total_wrestlers <- format(n_distinct(c(all_matches$winner, all_matches$loser)), big.mark = ",")
```

```{r}
#| echo: false
#| message: false
#| warning: false

leaflet(schools_geo, height = 380, width = "100%") |>
  addProviderTiles(providers$CartoDB.Positron) |>
  setView(lng = -98.35, lat = 39.5, zoom = 4) |>
  addCircleMarkers(
    lng = ~lng,
    lat = ~lat,
    radius = 6,
    color = "#2563eb",
    fillColor = "#3b82f6",
    fillOpacity = 0.85,
    stroke = TRUE,
    weight = 1.5,
    popup = ~paste0("<strong>", school, "</strong><br/>", city, ", ", state),
    label = ~paste0(school, " (", city, ", ", state, ")")
  )
```

::: {.grid .mb-4}

::: {.g-col-12 .g-col-md-4}
::: {.stat-card .card-blue}
<div class="stat-num">`r total_matches`</div>
<div class="stat-label">Total Matches</div>
:::
:::

::: {.g-col-12 .g-col-md-4}
::: {.stat-card .card-red}
<div class="stat-num">`r total_tournaments`</div>
<div class="stat-label">Tournaments (2019–2026)</div>
:::
:::

::: {.g-col-12 .g-col-md-4}
::: {.stat-card .card-blue}
<div class="stat-num">`r total_wrestlers`</div>
<div class="stat-label">Unique Wrestlers</div>
:::
:::

:::

::: {.panel-tabset}

## 👑 National Placers (1st–8th)

```{r}
#| echo: false
reactable(
  placers_df |> select(place, wrestler, school, weight_class, year, record, medal_bout),
  theme = tbl_theme,
  searchable = TRUE,
  filterable = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  defaultPageSize = 10,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(10, 20, 50, 80),
  rowStyle = \(index) {
    if (placers_df$place_num[index] == 1) {
      list(background = "#fffbeb", fontWeight = "600")
    }
  },
  columns = list(
    place = colDef(name = "Podium Finish", minWidth = 140, cell = badge_place),
    wrestler = colDef(
      name = "Wrestler",
      minWidth = 160,
      cell = \(value, index) {
        if (placers_df$place_num[index] == 1) {
          tags$span(style = "font-weight: 750; color: #0f172a;", paste0("⭐ ", value))
        } else {
          tags$span(value)
        }
      }
    ),
    school = colDef(name = "Collegiate Team", minWidth = 180),
    weight_class = colDef(name = "Weight", width = 95, align = "center", format = colFormat(suffix = " lbs")),
    year = colDef(name = "Year", width = 80, align = "center"),
    record = colDef(name = "Tourney Record", width = 125, align = "center"),
    medal_bout = colDef(name = "Medal Round Outcome", minWidth = 240)
  )
)
```

## 🏫 Team / State Search

```{r}
#| echo: false
reactable(
  school_legacy_table |> select(school, state, city, national_champions, all_americans, bouts_won, win_pct),
  theme = tbl_theme,
  searchable = TRUE,
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  defaultPageSize = 10,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(10, 20, 50),
  columns = list(
    school = colDef(name = "Collegiate Program", minWidth = 190),
    state = colDef(name = "State", width = 85, align = "center", cell = badge_state),
    city = colDef(name = "City", minWidth = 130),
    national_champions = colDef(name = "National Titles", width = 130, align = "center", cell = badge_champ_count),
    all_americans = colDef(name = "All-Americans", width = 130, align = "center", cell = badge_aa_count),
    bouts_won = colDef(name = "Bouts Won", width = 110, align = "center"),
    win_pct = colDef(name = "Win %", width = 90, align = "center")
  ),
  details = function(index) {
    sch_name <- school_legacy_table$school[index]
    sch_placers <- all_school_placers |> filter(school == sch_name) |> arrange(desc(year), place)
    champs <- sch_placers |> filter(grepl("1st", place))
    other_aa <- sch_placers |> filter(!grepl("1st", place))
    
    div(
      style = "padding: 10px 16px; background: #f8fafc; border-left: 4px solid #38bdf8; border-radius: 4px; margin: 4px 0;",
      if (nrow(champs) > 0) {
        div(
          tags$b(style = "color: #92400e;", "👑 National Champions: "),
          paste(sprintf("%s (%s, %s lbs)", champs$wrestler, champs$year, champs$weight_class), collapse = " • ")
        )
      },
      if (nrow(other_aa) > 0) {
        div(
          style = if (nrow(champs) > 0) "margin-top: 6px;" else "",
          tags$b(style = "color: #334155;", "🎖️ All-Americans: "),
          paste(sprintf("%s (%s - %s, %s lbs)", other_aa$wrestler, other_aa$place, other_aa$year, other_aa$weight_class), collapse = " • ")
        )
      },
      if (nrow(sch_placers) == 0) {
        div(style = "color: #64748b; font-style: italic;", "Emerging collegiate program / national competitor.")
      }
    )
  }
)
```

## 📈 Growth Explosion

::: {.grid .mb-3}

::: {.g-col-12 .g-col-md-4}
::: {.stat-card .card-blue}
<div class="stat-num">+100%</div>
<div class="stat-label">Program Growth</div>
<p style="font-size: 0.85rem; color: #64748b; margin-top: 0.5rem; margin-bottom: 0;">Surged from 20 inaugural colleges in 2019 to 40 varsity programs competing nationwide.</p>
:::
:::

::: {.g-col-12 .g-col-md-4}
::: {.stat-card .card-red}
<div class="stat-num">1st in USA</div>
<div class="stat-label">Championship Milestone</div>
<p style="font-size: 0.85rem; color: #64748b; margin-top: 0.5rem; margin-bottom: 0;">In 2023, NAIA became the first collegiate association in America to award full championship status.</p>
:::
:::

::: {.g-col-12 .g-col-md-4}
::: {.stat-card .card-blue}
<div class="stat-num">1,000+</div>
<div class="stat-label">National Athletes</div>
<p style="font-size: 0.85rem; color: #64748b; margin-top: 0.5rem; margin-bottom: 0;">Over a thousand collegiate women wrestlers have stepped onto the national championship mats.</p>
:::
:::

:::

```{r}
#| echo: false
#| message: false
#| warning: false
plot_ly(growth_df, x = ~factor(year), height = 430) |>
  add_bars(
    y = ~Colleges,
    name = "Colleges Fielded",
    text = ~paste0(Colleges, " schools"),
    textposition = "inside",
    insidetextanchor = "middle",
    textfont = list(color = "#ffffff", size = 12, family = "sans-serif"),
    marker = list(
      color = "#38bdf8",
      line = list(color = "#0284c7", width = 1.5)
    ),
    hovertemplate = "<b>Year %{x}</b><br>Colleges: %{y}<extra></extra>"
  ) |>
  add_lines(
    y = ~Athletes,
    name = "National Competitors",
    yaxis = "y2",
    line = list(color = "#ef4444", width = 3.5),
    marker = list(color = "#dc2626", size = 8),
    text = ~paste0(Athletes, " athletes"),
    textposition = "top center",
    textfont = list(color = "#b91c1c", size = 12, family = "sans-serif"),
    mode = "lines+markers+text",
    hovertemplate = "<b>Year %{x}</b><br>Athletes: %{y}<extra></extra>"
  ) |>
  layout(
    title = list(
      text = "<b>NAIA Women's Wrestling Participation Surge (2019–2026)</b>",
      font = list(size = 17, color = "#0f172a")
    ),
    xaxis = list(
      title = "<b>Championship Tournament Year</b>",
      tickfont = list(size = 13, color = "#1e293b"),
      titlefont = list(size = 13, color = "#334155")
    ),
    yaxis = list(
      title = "<b>Colleges Fielded (Bars)</b>",
      titlefont = list(color = "#0284c7", size = 13),
      tickfont = list(color = "#0284c7", size = 12),
      range = c(0, 55),
      gridcolor = "#f1f5f9"
    ),
    yaxis2 = list(
      title = "<b>National Competitors (Line)</b>",
      titlefont = list(color = "#dc2626", size = 13),
      tickfont = list(color = "#dc2626", size = 12),
      overlaying = "y",
      side = "right",
      range = c(0, 375),
      showgrid = FALSE
    ),
    legend = list(
      orientation = "h",
      x = 0.5,
      xanchor = "center",
      y = 1.12,
      font = list(size = 12)
    ),
    plot_bgcolor = "#ffffff",
    paper_bgcolor = "#ffffff",
    margin = list(t = 70, b = 50, l = 60, r = 60)
  )
```

::: {.grid .mt-4}

::: {.g-col-12 .g-col-md-6}
::: {.callout-note appearance="simple"}
## 📋 Note on 2023 Tournament Data
Official match-by-match bout logs and participant counts for the **2023 National Championship** were not available in the public tournament archives, so 2023 numbers are omitted from the timeline (similarly, the 2020 tournament was cancelled nationwide due to COVID-19).
:::
:::

::: {.g-col-12 .g-col-md-6}
::: {.callout-tip appearance="simple"}
## 🏫 Why School Numbers Shifted After 2022
Between 2022 and 2024, the tournament transitioned from an **open national invitational** to an **official championship sport**. In the open era (2019–2022), any school could enter multiple athletes, leading to an uncapped peak of 40 colleges in 2022. Beginning in 2024, NAIA instituted **strict conference qualifying tournaments** and capped brackets at 20 wrestlers per weight class, so only the top ~35–36 schools with automatic conference qualifiers advance to nationals.
:::
:::

:::

## Wrestler Rosters

```{r}
#| echo: false
reactable(
  roster_df,
  theme = tbl_theme,
  searchable = TRUE,
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  defaultPageSize = 15,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(10, 15, 25, 50, 100),
  columns = list(
    year = colDef(name = "Year", width = 85, align = "center"),
    weight_class = colDef(name = "Weight", width = 90, align = "center"),
    wrestler = colDef(name = "Wrestler", minWidth = 160),
    school = colDef(name = "School", minWidth = 160),
    record = colDef(name = "Record (W-L)", width = 120, align = "center"),
    place = colDef(name = "Tournament Finish", minWidth = 150, cell = badge_place)
  )
)
```

## Match Results

```{r}
#| echo: false
reactable(
  all_matches,
  theme = tbl_theme,
  searchable = TRUE,
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  defaultPageSize = 15,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(10, 15, 25, 50, 100),
  columns = list(
    year = colDef(name = "Year", width = 85, align = "center"),
    weight_class = colDef(name = "Weight", width = 90, align = "center"),
    round = colDef(name = "Round", minWidth = 140),
    winner = colDef(name = "Winner", minWidth = 140),
    winner_school = colDef(name = "Winner School", minWidth = 140),
    win_method = colDef(name = "Method", width = 110, align = "center", cell = badge_win_method),
    score = colDef(name = "Score / Time", minWidth = 100),
    loser = colDef(name = "Loser", minWidth = 140),
    loser_school = colDef(name = "Loser School", minWidth = 140)
  )
)
```

:::
